Supplementary Information -- Morphological convergence as on-line lexical analogy

### 2020-04-20 supplementary_information/si.tex
fix fig
Janet checked

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:57 2020
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
verb class & irregular set & regular set & miscellaneous regular verbs \\ 
  \hline
BURNT & 6 & 42 & 1218 \\ 
  DROVE & 14 & 83 & 1218 \\ 
  KEPT & 12 & 31 & 1218 \\ 
  SANG & 8 & 13 & 1218 \\ 
  count of unique forms & 40 & 169 & 1218 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, GCM training data} 
\label{gcmsetsize}
\end{table}
\subsection{Estimation}

@@

The MGL generates multiple possible past tense forms for each nonce verb. We only consider those rules {\em relevant} that generate the past tense forms that appear in the experiment (e.g.\ {\em splive} : {\em splived} / {\em splove}). There is at most one relevant regular rule and one relevant irregular rule for one verb, but multiple rules can generate the (ir)regular forms for each verb class. We return to this in the next section.

Note that the sets of exceptions and related forms of each rule can overlap, both respectively and with each other. As a consequence, the MGL rules apply to fewer forms than apparent from the table: 401 in total.

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:57 2020
\begin{table}[ht]
\centering
\begin{tabular}{llrr}
  \hline
category & rule.type & related forms & exceptions \\ 
  \hline
BURNT & irregular &  24 &  41 \\ 
  DROVE & irregular &  21 & 114 \\ 
  KEPT & irregular &  10 &   9 \\ 
  SANG & irregular &  11 &  77 \\ 
  BURNT & regular &  38 &  21 \\ 
  DROVE & regular &  29 &  27 \\ 
  KEPT & regular &  67 &  41 \\ 
  SANG & regular &  47 &  38 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, MGL training data} 
\label{mglsetsize}
\end{table}
\subsection{Estimation}

The MGL begins by considering the relationship between each verb and its past tense as a `rule'. For each pair of verbs in the training data, it then attempts to create a more general rule. It does so by aligning the wordforms and analyzing shared phonetic features. For example,  merging the word-specific rules for {\em ring/rang} and for {\em stink/stank} yields a more general rule that expresses the information that they share: \textipa{[I]} $\rightarrow{}$\textipa{[\ae]} / [+coronal, - cont] \underline{\hspace{0.5cm}} \textipa{[N]}. Each rule inferred in this way is then further generalized on the basis of more comparisons; for instance, taking note of {\em swim/swam} expands the \textipa{[I]} $\rightarrow{}$\textipa{[\ae]} rule to specify that it occurs before all [+nasal] consonants.

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:57 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
category & irregular rule & regular rule & sum \\ 
  \hline
burnt &   4 &   2 &   6 \\ 
  drove &  13 &   3 &  16 \\ 
  kept &   5 &   5 &  10 \\ 
  sang &  10 &   4 &  14 \\ 
   \hline
\end{tabular}
\caption{Number of regular and irregular rules in each verb class, posited by the MGL for the training data (Note that the regular rules themselves overlap)} 
\label{mglruletable}
\end{table}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:57 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -0.11 & 0.16 & -0.67 & n.s. \\ 
  verb\_baseline\_average & 8.26 & 0.69 & 12.04 & *** \\ 
  co\_player\_lexical\_typicalityrandom & 0.04 & 0.17 & 0.25 & n.s. \\ 
  co\_player\_lexical\_typicalityreversed & 0.04 & 0.17 & 0.20 & n.s. \\ 
  participant\_prereg\_average & 7.13 & 0.56 & 12.67 & *** \\ 
  co\_player\_regularisation\_rate-40\% & -0.46 & 0.18 & -2.47 & * \\ 
  co\_player\_regularisation\_rate+40\% & 0.55 & 0.17 & 3.31 & *** \\ 
  verb\_baseline\_average:co\_player\_lexical\_typicalityrandom & -2.40 & 0.93 & -2.59 & ** \\ 
  verb\_baseline\_average:co\_player\_lexical\_typicalityreversed & -2.13 & 0.96 & -2.23 & * \\ 
   \hline
\end{tabular}
\caption{Experimental Data, Post-test Regression Model Summary. Model formula: post-test regular response ~ verb baseline mean x lexical typicality + participant pretest mean + regularization shift + (1 + verb.baseline.mean | participant) + (1 | verb)} 
\label{regressiontable1}
\end{table}
Our regression model selection in this article proceeded as follows. Except where stated otherwise, we fit logistic mixed-effects regression models, using R's lme4 package \citep{bateslme4}. Non-significant predictors are removed from our models, as determined by a series of comparisons of nested models, using likelihood ratio tests in R's anova function. However, our model tables (e.g., Tables 5 and 6 in the main text) include the Wald significance levels generated by lme4 summaries (* p$<$0.05; ** p$<$0.01; *** p$<$0.001).  
We investigate maximal random effects structures, allowing for random intercepts for participants and stimulus items (verbs), as well as random slopes for all within-unit factors. We compare nested random effects structures as above, and retain any random slopes and intercepts which are supported by likelihood ratio tests \citep{baayen2008mixed}.

In the model in Table 5 in the main text, repeated here as Table \ref{regressiontable1}, we elect to mean center continuous variables to counteract collinearity that becomes evident when including the interaction between and {\em lexical typicality}.  Although some debate exists regarding the practice of transforming variables \citep{belsley1991conditioning,echambadi2007mean}, centering variables is common practice to remove nonessential ill conditioning, that is, relationships that inevitably exist between main and product terms \citep{aiken1991multiple,jaccard2003interaction, jaeger2008categorical}. We note that if {\em verb baseline mean} is {\em not} centered, collinearity is high (VIF=15.79) in this model. A non-centered model also yields a significant main effect for {\em lexical typicality}, with increased post-test regularization in the random and reversed conditions. However, we elect to take a more conservative approach by not including a potentially spurious main effect. Note that other than this main effect difference, models with and without centering yield results that are qualitatively indistinguishable; all other main effects and interactions are present in either case. The collinearity for the centered model (Table 5 in the main text) is acceptable, with a maximum VIF score of 2.9.

Since it is unclear whether the absence of a difference between random and reversed conditions is due to a lack of data, we refit the model with the baseline average : typicality interaction on the random and reversed conditions only. Then we calculated the Bayes Factor of the null model (with no interaction) over the full model (with interaction) using Bayesian Information Criteria calculated by lme4. The result strongly supports the null model over the full model, indicating that the preference for the null model is {\em not} due to the lack of evidence to reject it.

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:58 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -0.53 & 0.12 & -4.22 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.35 & 0.09 & 14.48 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance\_residual & 1.42 & 0.13 & 11.10 & *** \\ 
   \hline
\end{tabular}
\caption{Model 3: MGL scores and GCM residuals, baseline data} 
\label{resid1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:58 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -1.23 & 0.16 & -7.68 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 2.39 & 0.15 & 16.06 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance\_residual & 1.01 & 0.09 & 11.15 & *** \\ 
   \hline
\end{tabular}
\caption{Model 4: GCM scores and MGL residuals, baseline data} 
\label{resid2}
\end{table}
Model 1 predicts the GCM scores from the MGL scores (M1: GCM regular score  $\sim$ MGL regular score). Model 2 predicts the MGL scores from the GCM scores (M2: MGL regular score  $\sim$ GCM regular score). In two additional models, we then use the residuals from each model (M1, M2) as an estimate of the variation present in one score that cannot be attributed to the other.  First, we use the residuals of Model 1 in another, mixed-effects logistic regression model along with the MGL scores to predict regular responses in the baseline task (M3: regular response  $\sim$ MGL score + GCM residual + (1 + MGL score + GCM residual$|$participant) + (1 $|$ verb)). We then residualize for the MGL. We use the residuals of Model 2 along with the GCM scores in a similar logistic regression model (M4: regular response  $\sim$ GCM score + MGL residual + (1 + GCM score + MGL residual $|$participant)).

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:58 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -2.95 & 0.29 & -10.01 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 4.37 & 0.42 & 10.28 & *** \\ 
  gcm\_score\_diff & 2.61 & 0.47 & 5.56 & *** \\ 
  participant\_prereg\_average & 5.29 & 0.60 & 8.79 & *** \\ 
   \hline
\end{tabular}
\caption{Model 5: Celex-GCM and individual score difference, post-test data} 
\label{indiv1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:58 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -1.32 & 0.15 & -8.66 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.94 & 0.18 & 11.04 & *** \\ 
  mgl\_score\_diff & 0.30 & 0.14 & 2.18 & * \\ 
  participant\_prereg\_average & 7.20 & 0.59 & 12.19 & *** \\ 
   \hline
\end{tabular}
\caption{Model 6: Celex-MGL and individual score difference, post-test data} 
\label{indiv2}
\end{table}
We do this for both the GCM  (Model 5: regular response  $\sim$ \textsc{Celex} GCM score + extra GCM information + participant pre-test mean + (1 + \textsc{Celex} GCM + extra GCM information$|$participant) + (1$|$verb) and the MGL (Model 6: regular response  $\sim$ \textsc{Celex} MGL score + extra MGL information + participant pre-test mean + (1 + \textsc{Celex} MGL + extra MGL information$|$participant)+ (1$|$verb)).

@@

We used the {\sc Celex}-GCM, {\sc Celex}-MGL, individual-GCM, and individual-MGL together to predict participant post-test responses. The best model, reported in the paper, contains the {\sc Celex}-MGL and the individal-GCM. The summary can be seen in Table \ref{comp3}.

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Tue Mar  3 13:14:59 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -2.94 & 0.27 & -10.90 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.60 & 0.17 & 9.36 & *** \\ 
  rescaled\_individual\_gcm\_feature\_distance & 2.79 & 0.38 & 7.37 & *** \\ 
  participant\_prereg\_average & 5.44 & 0.58 & 9.30 & *** \\ 
   \hline
\end{tabular}
\caption{Celex-MGL and Individual-GCM predict variation in the post-test} 
\label{comp3}
\end{table}
Goodness-of-fit tests show that model fit is significantly worse if we exclude {\sc Celex}-MGL ($\chi^2 = $ 201.86 ***) or individual-GCM ($\chi^2 = $ 81.82 ***) as predictors. It is not significantly better if we include individual-MGL ($\chi^2 = $ 0.09, p = 0.77) or {\sc Celex}-GCM ($\chi^2 = $ 2.03, p = 0.15).

>>>>

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
verb class & irregular set & regular set & miscellaneous regular verbs \\ 
  \hline
BURNT & 6 & 42 & 1218 \\ 
  DROVE & 14 & 83 & 1218 \\ 
  KEPT & 12 & 31 & 1218 \\ 
  SANG & 8 & 13 & 1218 \\ 
  count of unique forms & 40 & 169 & 1218 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, GCM training data} 
\label{gcmsetsize}
\end{table}
\subsection{Estimation}

@@

The MGL generates multiple possible past tense forms for each nonce verb. We only consider to be {\em relevant} those rules that generate the past tense forms that appear in the experiment (e.g.\ {\em splive} : {\em splived} / {\em splove}). There is at most one relevant regular rule and one relevant irregular rule for one verb, but multiple rules can generate the (ir)regular forms for each verb class. We return to this in the next section.

Note that the sets of exceptions and related forms of each rule can overlap.  As a consequence, the MGL rules apply to fewer forms than apparent from the table: 401 in total.

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{llrr}
  \hline
category & rule.type & related forms & exceptions \\ 
  \hline
BURNT & irregular &  24 &  41 \\ 
  DROVE & irregular &  21 & 114 \\ 
  KEPT & irregular &  10 &   9 \\ 
  SANG & irregular &  11 &  77 \\ 
  BURNT & regular &  38 &  21 \\ 
  DROVE & regular &  29 &  27 \\ 
  KEPT & regular &  67 &  41 \\ 
  SANG & regular &  47 &  38 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, MGL training data} 
\label{mglsetsize}
\end{table}
\subsection{Estimation}

The MGL begins by considering the relationship between each verb and its past tense as a `rule'. For each pair of verbs in the training data, it then attempts to create a more general rule. It does so by aligning the wordforms and analyzing shared phonetic features. For example,  merging the word-specific rules for {\em ring/rang} and for {\em stink/stank} yields a more general rule that expresses the information that they share: \textipa{[I]} $\rightarrow{}$\textipa{[\ae]} / [+coronal] \underline{\hspace{0.5cm}} \textipa{[N]}. Each rule inferred in this way is then further generalized on the basis of more comparisons; for instance, taking note of {\em swim/swam} expands the \textipa{[I]} $\rightarrow{}$\textipa{[\ae]} rule to specify that it occurs before all [+nasal] consonants.

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
category & irregular rule & regular rule & sum \\ 
  \hline
burnt &   4 &   2 &   6 \\ 
  drove &  13 &   3 &  16 \\ 
  kept &   5 &   5 &  10 \\ 
  sang &  10 &   4 &  14 \\ 
   \hline
\end{tabular}
\caption{Number of regular and irregular rules in each verb class, posited by the MGL for the training data (Note that the regular rules themselves overlap)} 
\label{mglruletable}
\end{table}

@@

Our regression model selection in this article proceeded as follows. Except where stated otherwise, we fit logistic mixed-effects regression models, using R's lme4 package \citep{bateslme4}. Non-significant predictors are removed from our models, as determined by a series of comparisons of nested models, using likelihood ratio tests in R's anova function. However, our model tables (e.g., Tables 5 and 6 in the main text) include the Wald significance levels generated by lme4 summaries (* p$<$0.05; ** p$<$0.01; *** p$<$0.001).  
We investigate maximal random effects structures, allowing for random intercepts for participants and stimulus items (verbs), as well as random slopes for all within-unit factors. We compare nested random effects structures as above, and retain any random slopes and intercepts which are supported by likelihood ratio tests \citep{baayen2008mixed}.

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -0.11 & 0.16 & -0.67 & n.s. \\ 
  verb\_baseline\_average & 8.26 & 0.69 & 12.04 & *** \\ 
  co\_player\_lexical\_typicalityrandom & 0.04 & 0.17 & 0.25 & n.s. \\ 
  co\_player\_lexical\_typicalityreversed & 0.04 & 0.17 & 0.20 & n.s. \\ 
  participant\_prereg\_average & 7.13 & 0.56 & 12.67 & *** \\ 
  co\_player\_regularisation\_rate-40\% & -0.46 & 0.18 & -2.47 & * \\ 
  co\_player\_regularisation\_rate+40\% & 0.55 & 0.17 & 3.31 & *** \\ 
  verb\_baseline\_average:co\_player\_lexical\_typicalityrandom & -2.40 & 0.93 & -2.59 & ** \\ 
  verb\_baseline\_average:co\_player\_lexical\_typicalityreversed & -2.13 & 0.96 & -2.23 & * \\ 
   \hline
\end{tabular}
\caption{Experimental Data, Post-test Regression Model Summary. Model formula: post-test regular response ~ verb baseline mean x lexical typicality + participant pretest mean + regularization shift + (1 + verb.baseline.mean | participant) + (1 | verb)} 
\label{regressiontable1}
\end{table}
In the model in Table 5 in the main text, repeated here as Table \ref{regressiontable1}, we elect to mean center continuous variables to counteract collinearity that becomes evident when including the interaction between {\em verb baseline average} and {\em lexical typicality}.  Although some debate exists regarding the practice of transforming variables \citep{belsley1991conditioning,echambadi2007mean}, centering variables is common practice to remove nonessential ill conditioning, that is, relationships that inevitably exist between main and product terms \citep{aiken1991multiple,jaccard2003interaction, jaeger2008categorical}. We note that if {\em verb baseline mean} is {\em not} centered, collinearity is high (VIF=15.79) in this model. A non-centered model also yields a significant main effect for {\em lexical typicality}, with increased post-test regularization in the random and reversed conditions. However, we elect to take a more conservative approach by not including a potentially spurious main effect. Note that other than this main effect difference, models with and without centering yield results that are qualitatively indistinguishable; all other main effects and interactions are present in either case. The collinearity for the centered model (Table 5 in the main text) is acceptable, with a maximum VIF score of 2.9.

Since it is unclear whether the absence of a difference between random and reversed conditions is due to a lack of data, we refit the model with the {\em verb baseline average : lexical typicality} interaction on the random and reversed conditions only. Then we calculated the Bayes Factor of the null model (with no interaction) over the full model (with interaction) using Bayesian Information Criteria calculated by lme4. The result strongly supports the null model over the full model, indicating that the preference for the null model is {\em not} due to the lack of evidence to reject it.

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:27 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -0.53 & 0.12 & -4.22 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.35 & 0.09 & 14.48 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance\_residual & 1.42 & 0.13 & 11.10 & *** \\ 
   \hline
\end{tabular}
\caption{Model 3: MGL scores and GCM residuals, baseline data} 
\label{resid1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:27 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -1.23 & 0.16 & -7.68 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 2.39 & 0.15 & 16.06 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance\_residual & 1.01 & 0.09 & 11.15 & *** \\ 
   \hline
\end{tabular}
\caption{Model 4: GCM scores and MGL residuals, baseline data} 
\label{resid2}
\end{table}
Model 1 predicts the GCM scores from the MGL scores (M1: GCM regular score  $\sim$ MGL regular score). Model 2 predicts the MGL scores from the GCM scores (M2: MGL regular score  $\sim$ GCM regular score). In two additional models, we then use the residuals from each model (M1, M2) as an estimate of the variation present in one score that cannot be attributed to the other.  First, we use the residuals of Model 1 in another, mixed-effects logistic regression model along with the MGL scores to predict regular responses in the baseline task (M3: regular response  $\sim$ MGL score + GCM residual + (1 + MGL score + GCM residual$|$participant) + (1 $|$ verb)). We then residualize for the MGL. We use the residuals of Model 2 along with the GCM scores in a similar logistic regression model (M4: regular response  $\sim$ GCM score + MGL residual + (1 + GCM score + MGL residual $|$participant)).

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:27 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -2.95 & 0.29 & -10.01 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 4.37 & 0.42 & 10.28 & *** \\ 
  gcm\_score\_diff & 2.61 & 0.47 & 5.56 & *** \\ 
  participant\_prereg\_average & 5.29 & 0.60 & 8.79 & *** \\ 
   \hline
\end{tabular}
\caption{Model 5: Celex-GCM and individual score difference, post-test data} 
\label{indiv1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:27 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -1.32 & 0.15 & -8.66 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.94 & 0.18 & 11.04 & *** \\ 
  mgl\_score\_diff & 0.30 & 0.14 & 2.18 & * \\ 
  participant\_prereg\_average & 7.20 & 0.59 & 12.19 & *** \\ 
   \hline
\end{tabular}
\caption{Model 6: Celex-MGL and individual score difference, post-test data} 
\label{indiv2}
\end{table}
We do this for both the GCM  (Model 5: regular response  $\sim$ \textsc{Celex} GCM score + extra GCM information + participant pre-test mean + (1 + \textsc{Celex} GCM + extra GCM information$|$participant) + (1$|$verb) and the MGL (Model 6: regular response  $\sim$ \textsc{Celex} MGL score + extra MGL information + participant pre-test mean + (1 + \textsc{Celex} MGL + extra MGL information$|$participant)+ (1$|$verb)).

@@

We used the {\sc Celex}-GCM, {\sc Celex}-MGL, individual-GCM, and individual-MGL together to predict participant post-test responses. The best model, reported in the paper, contains the {\sc Celex}-MGL and the individal-GCM. The summary can be seen in Table \ref{comp3}. This is the model we report in detail in the main text.

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:28 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -2.94 & 0.27 & -10.90 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.60 & 0.17 & 9.36 & *** \\ 
  rescaled\_individual\_gcm\_feature\_distance & 2.79 & 0.38 & 7.37 & *** \\ 
  participant\_prereg\_average & 5.44 & 0.58 & 9.30 & *** \\ 
   \hline
\end{tabular}
\caption{Celex-MGL and Individual-GCM predict variation in the post-test} 
\label{comp3}
\end{table}
Goodness-of-fit tests show that model fit is significantly worse if we exclude {\sc Celex}-MGL ($\chi^2 = $ 201.86 ***) or individual-GCM ($\chi^2 = $ 81.82 ***) as predictors. It is not significantly better if we include individual-MGL ($\chi^2 = $ 0.09, p = 0.77) or {\sc Celex}-GCM ($\chi^2 = $ 2.03, p = 0.15).
